Covid-19 Fields Survey Data Protocol

### 2023-02-02 protocol/Background_and_methods_Jan_24.qmd
updated file

For each survey participant certain data was automatically captured. This included the nearest municipality, which resulted in a total of 578 different municipalities within the dataset. Because our interest was to analyze the differences between Health Regions, we assigned the location (city) of each entry to its correspondent Health Region following a multi-step process: First, we used the municipality information from the website of the Association of Municipalities of Ontario (AMO) to assign geographical regions to each entry on the dataset. Secondly, we used a publicly available dataset of long-term care homes by Local Health Integrated Network (LHIN), which were the geographical divisions for health in Ontario before the adoption of the Health Regions, to match each city with its corresponding LHIN. Cities that did not have a LHIN entry on the dataset were searched in the websites of the LHINs and manually added to the dataset. Finally, we assigned the corresponding Health Region to each city by matching the LHINs to the Health Regions that now encompass them, following the information provided by Ontario Health (details of the complete process are in the Appendix).

Following an assessment of the number of entries corresponding to each Health Region in the clean dataset, there were a relatively low number of observations from the North East and North West regions (2.9% and 1.4% of the total clean dataset, respectively). Due to the low number of entries in each case, we omitted the entries from these regions from further analyses. Therefore, the total number of unique entries used for analysis was 3,551.

>>>>

For each survey participant certain data was automatically captured. This included the nearest municipality, which resulted in a total of 578 different municipalities within the dataset. Due to our interest in analyzing the differences between Health Regions, we assigned the location (city) of each entry to its correspondent Health Region following a multi-step process: First, we used the municipality information from the website of the Association of Municipalities of Ontario (AMO) to assign geographical regions to each entry on the dataset. Secondly, we used a publicly available dataset of long-term care homes by Local Health Integrated Network (LHIN, the previous geographical divisions for health in Ontario before the adoption of the Health Regions), to match each city with its corresponding LHIN. Cities that did not have a LHIN entry on the dataset were searched in the websites of the LHINs and manually added to the dataset. Finally, we assigned the corresponding Health Region to each city by matching the LHINs to the Health Regions that now encompass them, following the information provided by Ontario Health (details of the complete process are in the Appendix).

Following an assessment of the number of entries corresponding to each Health Region in the clean dataset, we removed entries that corresponded to the North East and North West Health Regions as they comprised only 107 observations (4.3% of the total). Due to the low number of entries in these regions, we omitted these Health Regions from further analyses. Therefore, the total number of unique entries used for analysis was 3,551 comprising the East, Central, Toronto, and West Health Regions.

### 2023-02-02 protocol/Background_and_methods_Jan_24.tex
updated file

\title{Covid-19 Fields Survey Data Protocol}
\author{Ariel Mundo Ortiz}
\date{1/24/23}

\begin{document}
\maketitle
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, borderline west={3pt}{0pt}{shadecolor}, sharp corners, boxrule=0pt, enhanced, breakable, frame hidden]}{\end{tcolorbox}}\fi

@@

For each survey participant certain data was automatically captured.
This included the nearest municipality, which resulted in a total of 578
different municipalities within the dataset. Because our interest was to
analyze the differences between Health Regions, we assigned the location
(city) of each entry to its correspondent Health Region following a
multi-step process: First, we used the municipality information from the
website of the Association of Municipalities of Ontario (AMO) to assign
geographical regions to each entry on the dataset. Secondly, we used a
publicly available dataset of long-term care homes by Local Health
Integrated Network (LHIN), which were the geographical divisions for
health in Ontario before the adoption of the Health Regions, to match
each city with its corresponding LHIN. Cities that did not have a LHIN
entry on the dataset were searched in the websites of the LHINs and
manually added to the dataset. Finally, we assigned the corresponding
Health Region to each city by matching the LHINs to the Health Regions
that now encompass them, following the information provided by Ontario
Health (details of the complete process are in the Appendix).

Following an assessment of the number of entries corresponding to each
Health Region in the clean dataset, there were a relatively low number
of observations from the North East and North West regions (2.9\% and
1.4\% of the total clean dataset, respectively). Due to the low number
of entries in each case, we omitted the entries from these regions from
further analyses. Therefore, the total number of unique entries used for
analysis was 3,551.

@@

Table~\ref{tbl-model} shows the results of the logistic regression on
vaccination status using socio-economic, geographical factors (by Health
Region) and their interactions as predictors. The reference groups in
each case were set as follow: 16 to 24 years (age group), White
Caucasian (Race), Toronto (Health Region), Over CAD 90,000 (Income).
Socio-economic factors with statistically significant odds ratios were
the age group of 65 years and over (OR=0.58), persons who identified as
Arab/Middle Eastern (OR=0.15), Black (OR=0.17), Indigenous (OR=0.27),
Latin American (OR=0.24), South Asian (OR=0.17) and Other Race/Ethnicity
(a group that included minorities not found elsewhere, OR=0.17), and
those that lived in a household with an income bracket between CAD
25,000 and CAD 39,999.

Regarding the interaction of socio-economic and geographical factors,
statistically significant odds ratios were the Central Health Region and
Income of 15000 to 24999 CAD (OR=0.4), Age Group of 65 years and older
with a household income between 25000 and 39999 CAD (OR=0.001), and with
an income between 40000 and 59999 (OR=3.12)

>>>>

\title{Covid-19 Fields Survey Data Protocol}
\author{Ariel Mundo Ortiz}
\date{1/31/23}

\begin{document}
\maketitle
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, borderline west={3pt}{0pt}{shadecolor}, sharp corners, enhanced, breakable, frame hidden, boxrule=0pt]}{\end{tcolorbox}}\fi

@@

For each survey participant certain data was automatically captured.
This included the nearest municipality, which resulted in a total of 578
different municipalities within the dataset. Due to our interest in
analyzing the differences between Health Regions, we assigned the
location (city) of each entry to its correspondent Health Region
following a multi-step process: First, we used the municipality
information from the website of the Association of Municipalities of
Ontario (AMO) to assign geographical regions to each entry on the
dataset. Secondly, we used a publicly available dataset of long-term
care homes by Local Health Integrated Network (LHIN, the previous
geographical divisions for health in Ontario before the adoption of the
Health Regions), to match each city with its corresponding LHIN. Cities
that did not have a LHIN entry on the dataset were searched in the
websites of the LHINs and manually added to the dataset. Finally, we
assigned the corresponding Health Region to each city by matching the
LHINs to the Health Regions that now encompass them, following the
information provided by Ontario Health (details of the complete process
are in the Appendix).

Following an assessment of the number of entries corresponding to each
Health Region in the clean dataset, we removed entries that corresponded
to the North East and North West Health Regions as they comprised only
107 observations (4.3\% of the total). Due to the low number of entries
in these regions, we omitted these Health Regions from further analyses.
Therefore, the total number of unique entries used for analysis was
3,551 comprising the East, Central, Toronto, and West Health Regions.

@@

Table~\ref{tbl-model} shows the results of the logistic regression on
vaccination status using socio-economic, geographical factors (by Health
Region) and their interactions as predictors. The reference groups in
each case were set as follows: 16 to 24 years (age group), White
Caucasian (Race), Toronto (Health Region), Over CAD 90,000 (Income).
Socio-economic factors with statistically significant odds ratios were
the age group of 65 years and over (OR=0.44), persons who identified as
Arab/Middle Eastern (OR=0.15), Black (OR=0.17), Indigenous (OR=0.27),
Latin American (OR=0.24), South Asian (OR=0.4) and Other Race/Ethnicity
(a group that included minorities not found elsewhere, OR=0.17), and
those that lived in a household with an income bracket between CAD
25,000-39,999 (OR=0.23).

Regarding the interaction effects, the interaction of the Central Health
Region and income bracket between 15000 to 24999 CAD was statistically
significant (OR=0.4). In age group and income, significant effects were
estimated for those 65 years and older with a household income between
CAD 25000-39999 (OR=7.21), and with an income between CAD 40000-59999
(OR=3.12). In the case of race and income, significant effects were
estimated for individuals that identified as Arab/Middle Easterners with
a family income between 15000 and 24999 (OR=5.68) or income under CAD
15000 (OR=4.21), Black individuals with a family income under CAD 15000
(OR=4.26) or between CAD 15000-24999 (OR=3.35); additionally, there were
statistically significant interaction effects in the case of those that
identified as belonging to a race not identified elsewhere (``Other'')
within multiple income brackets: under CAD 15000 (OR=3.73), between
15000 and 24999 (OR 11.2), between 25000 and 39999 CAD (OR=4.67), and
with income CAD 40000-59999 (OR=9.58). Finally, there was a significant
interaction effect for South Asian individuals with an income under CAD
15000 (OR=3.10).
